Popularity Adjusted Block Models are Generalized Random Dot Product Graphs

### 2022-07-19 jsm/speed-presentation/poster/poster.Rmd
changes to poster based on meeting

## Popularity Adjusted Block Model

@@

**Theorem**: $\max_i \| \hat{x}_i - Q_n x_i \| = O_P \Big( \frac{\log^c n}{n^{1/2}} \Big)$ for some $Q_n \in \mathbb{O}(p, q)$.

@@

sbm.graph.plot <- ggraph(A, layout = 'stress') + 
  geom_edge_link(alpha = 1 / sqrt(n) / 2) + 
  geom_node_point(aes(colour = factor(z)),
                  show.legend = FALSE) + 
  labs(colour = NULL, 
       title = 'Stochastic Block Model') + 
  # theme_graph() + 
  theme_void() + 
  scale_colour_brewer(palette = 'Set1')

@@

dcbm.graph.plot <- ggraph(A, layout = 'stress') + 
  geom_edge_link(alpha = 1 / sqrt(n) / 2) + 
  geom_node_point(aes(colour = factor(z)),
                  show.legend = FALSE) + 
  labs(colour = NULL, 
       title = 'Degree Corrected Block Model') + 
  # theme_graph() + 
  theme_void() + 
  scale_colour_brewer(palette = 'Set1')

@@

pabm.graph.plot <- ggraph(A, layout = 'stress') + 
  geom_edge_link(alpha = 1 / sqrt(n) / 2) + 
  geom_node_point(aes(colour = factor(z)),
                  show.legend = FALSE) + 
  labs(colour = NULL, 
       title = 'Popularity Adjusted Block Model') + 
  # theme_graph() + 
  theme_void() + 
  scale_colour_brewer(palette = 'Set1')

@@

1. Eigendecompose $A \approx V_{p,q} \Lambda_{p,q} V_{p,q}^\top$ with $p = \frac{K (K+1)}{2}$ and $q = \frac{K (K-1)}{2}$.
2. Compute $B = |n V_{p,q} V_{p,q}^\top|$.
3. Construct graph $G'$ from $B$.
4. Partition $G'$ into $K$ disconnected subgraphs.

**Theorem** (KTT): 
Let $B$ be the affinity matrix from OSC. 
Then $\forall$ $(i, j)$ belonging to different communities and sparsity factor satisfying $n \rho_n = \omega\big(\log^{4c} n\big),$ $\max_{i, j} B_{ij} = O_P \Big( \frac{\log^c n}{\sqrt{n \rho_n}} \Big)$.

@@

```{r, fig.height = 2, fig.width = 5, out.width = '100%'}
clustering.df <- readr::read_csv('~/dev/pabm-grdpg/simulation-results/cluster-sim-balanced.csv')

>>>>

## Popularity Adjusted Block Model (Sengupta and Chen 2018)

@@

**Theorem** (Rubin-Delanchy et al. 2022): $\max_i \| \hat{x}_i - Q_n x_i \| = O_P \Big( \frac{\log^c n}{n^{1/2}} \Big)$ for some $Q_n \in \mathbb{O}(p, q)$.

@@

sbm.graph.plot <- ggraph(A, layout = 'stress') + 
  geom_edge_link(alpha = 1 / sqrt(n) / 2) + 
  geom_node_point(aes(colour = factor(z)),
                  show.legend = FALSE) + 
  labs(colour = NULL, 
       title = 'SBM') + 
  # theme_graph() + 
  theme_void() + 
  scale_colour_brewer(palette = 'Set1')

@@

dcbm.graph.plot <- ggraph(A, layout = 'stress') + 
  geom_edge_link(alpha = 1 / sqrt(n) / 2) + 
  geom_node_point(aes(colour = factor(z)),
                  show.legend = FALSE) + 
  labs(colour = NULL, 
       title = 'DCBM') + 
  # theme_graph() + 
  theme_void() + 
  scale_colour_brewer(palette = 'Set1')

@@

pabm.graph.plot <- ggraph(A, layout = 'stress') + 
  geom_edge_link(alpha = 1 / sqrt(n) / 2) + 
  geom_node_point(aes(colour = factor(z)),
                  show.legend = FALSE) + 
  labs(colour = NULL, 
       title = 'PABM') + 
  # theme_graph() + 
  theme_void() + 
  scale_colour_brewer(palette = 'Set1')

@@

1. Set $p = \frac{K (K+1)}{2}$, $q = \frac{K (K-1)}{2}$ and decompose $A \approx V_{p,q} \Lambda_{p,q} V_{p,q}^\top$.
2. Construct graph $G'$ from $B = |n V_{p,q} V_{p,q}^\top|$.
3. Partition $G'$ into $K$ disconnected subgraphs.

**Theorem** (KTT): 
$\max\limits_{i, j} B_{ij} = O_P \Big( \frac{\log^c n}{\sqrt{n \rho_n}} \Big)$ for each $(i, j)$ in different communities.

**Corollary**: OSC results in zero community detection error with probability 1 as $n \to \infty$.

@@

```{r, fig.height = 2.25, fig.width = 5, out.width = '100%'}
clustering.df <- readr::read_csv('~/dev/pabm-grdpg/simulation-results/cluster-sim-balanced.csv')
